Enhancing Adversarial Robustness for Deep Metric Learning

### 2022-01-30 reb/RebuttalTemplate.tex

\noindent\textbf{Q2.}
%
\ul{
Tables are hard to grasp at a first glance due to too many abbreviations and
notations.
}

\noindent\textbf{A:} Thanks for the suggestion.
In the next revision, we will (1) extend the captions to make them
self-explanatory; (2) repeat the definitions of symbols and abbreviations in
captions; (3) highlight the columns for important performance metrics
(\emph{i.e.}, R@1 and ERS); (4) colorize the abbreviations for different
defense methods in the same color as their corresponding legends in the
performance curve figures.

\noindent\textbf{Q3.}
%
\ul{
Comparison in memory and time complexity between defense methods is missing. Are they all
equal?
}

\noindent\textbf{A:}
%
They do not equal but only lead to minor difference in practice.
%
We conduct experiments with two ``Nvidia TITAN Xp'' GPUs on the CUB dataset
with $\eta{=}32$, as follows:
%
\noindent%
\resizebox{1.0\columnwidth}{!}{
\begin{tabular}{c|c|c|c|c}
	\toprule
	 & EST[$\mathcal{S}$]
	 & ACT[$\mathcal{S}$]
	 & HM[$\mathcal{S},g_\mathsf{LGA}$]
	 & HM[$\mathcal{S},g_\mathsf{LGA}$]\&ICS \\
	 \midrule
	Time Complexity
	& $\mathcal{O}_\mathsf{PGD} + \mathcal{O}_\mathsf{sampler}$
	& $\mathcal{O}_\mathsf{PGD} + \mathcal{O}_\mathsf{sampler}$
	&
	& \\
	Actual Training Time
	& 8.4 hour 
	& hour
	& 9.1 hour
	& 9.4 hour \\
	\hline
	Space Complexity 
	&
	&
	&
	& \\
	GPU Memory Usage 
	& 6559 MB
	& 6617 MB
	& 6657 MB
	& 8385 MB\\
	\bottomrule
\end{tabular}
	}
%
The PGD complexities per adversarial
example are identical across different defenses.
%
Triplet sampler is aligned in the table for identical
sampling complexities.
%
Omitting the identical terms, the rest stem from adversarial perturbation objective functions and loss function.
%
The reported values are uneasy to compare for future work as they are sensitive
to hardware, software, and programming tricks.
%
The paragraph will be provided in the next revision.

### 2022-01-30 reb/RebuttalTemplate.tex

\noindent\textbf{Q2.}
%
\ul{
Tables are hard to grasp at a first glance due to too many abbreviations and
notations.
}

\noindent\textbf{A:} Thanks for the suggestion.
In the next revision, we will (1) extend the captions to make them
self-explanatory; (2) repeat the definitions of symbols and abbreviations in
captions; (3) highlight the columns for important performance metrics
(\emph{i.e.}, R@1 and ERS); (4) colorize the abbreviations for different
defense methods in the same color as their corresponding legends in the
performance curve figures.

\noindent\textbf{Q3.}
%
\ul{
Comparison in memory and time complexity between defense methods is missing. Are they all
equal?
}

\noindent\textbf{A:}
%
They do not equal but only lead to minor difference in practice.
%
We conduct experiments with two ``Nvidia TITAN Xp'' GPUs on the CUB dataset
with $\eta{=}32$, as follows:
%
\noindent%
\resizebox{1.0\columnwidth}{!}{
\begin{tabular}{c|c|c|c|c}
	\toprule
	 & EST[$\mathcal{S}$]
	 & ACT[$\mathcal{S}$]
	 & HM[$\mathcal{S},g_\mathsf{LGA}$]
	 & HM[$\mathcal{S},g_\mathsf{LGA}$]\&ICS \\
	 \midrule
	Time Complexity
	& $\mathcal{O}(D)$
	& $\mathcal{O}_\mathsf{PGD} + \mathcal{O}_\mathsf{sampler}$
	&
	& \\
	Actual Training Time
	& 8.4 hour 
	& hour
	& 9.1 hour
	& 9.4 hour \\
	\hline
	Space Complexity 
	& $\mathcal{O}(D)$
	&
	&
	& \\
	GPU Memory Usage 
	& 6559 MB
	& 6617 MB
	& 6657 MB
	& 8385 MB\\
	\bottomrule
\end{tabular}
	}
%
The PGD complexities per adversarial
example are identical across different defenses.
%
Triplet sampler is aligned in the table for identical
sampling complexities.
%
Omitting the identical terms, the rest stem from adversarial perturbation objective functions and loss function.
%
The reported values are uneasy to compare for future work as they are sensitive
to hardware, software, and programming tricks.
%
The paragraph will be provided in the next revision.

### 2022-01-30 reb/RebuttalTemplate.tex

\noindent\textbf{Q2.}
%
\ul{
Tables are hard to grasp at a first glance due to too many abbreviations and
notations.
}

\noindent\textbf{A:} Thanks for the suggestion.
In the next revision, we will (1) extend the captions to make them
self-explanatory; (2) repeat the definitions of symbols and abbreviations in
captions; (3) highlight the columns for important performance metrics
(\emph{i.e.}, R@1 and ERS); (4) colorize the abbreviations for different
defense methods in the same color as their corresponding legends in the
performance curve figures.

\noindent\textbf{Q3.}
%
\ul{
Comparison in memory and time complexity between defense methods is missing. Are they all
equal?
}

\noindent\textbf{A:}
%
They do not equal but only lead to minor difference in practice.
%
We conduct experiments with two ``Nvidia TITAN Xp'' GPUs on the CUB dataset
with $\eta{=}32$, as follows:
%
\noindent%
\resizebox{1.0\columnwidth}{!}{
\begin{tabular}{c|c|c|c|c}
	\toprule
	 & EST[$\mathcal{S}$]
	 & ACT[$\mathcal{S}$]
	 & HM[$\mathcal{S},g_\mathsf{LGA}$]
	 & HM[$\mathcal{S},g_\mathsf{LGA}$]\&ICS \\
	 \midrule
	Time Complexity
	& $\mathcal{O}(\eta D)$
	& $\mathcal{O}(\eta D)$
	&
	& \\
	Actual Training Time
	& 8.4 hour 
	& hour
	& 9.1 hour
	& 9.4 hour \\
	\hline
	Space Complexity 
	& $\mathcal{O}(\eta D)$
	& $\mathcal{O}(\eta D)$
	&
	& \\
	GPU Memory Usage 
	& 6559 MB
	& 6617 MB
	& 6657 MB
	& 8385 MB\\
	\bottomrule
\end{tabular}
	}
%
The PGD complexities per adversarial
example are identical across different defenses.
%
Triplet sampler is aligned in the table for identical
sampling complexities.
%
Omitting the identical terms, the rest stem from adversarial perturbation objective functions and loss function.
%
The reported values are uneasy to compare for future work as they are sensitive
to hardware, software, and programming tricks.
%
The paragraph will be provided in the next revision.

### 2022-01-30 reb/RebuttalTemplate.tex

\noindent\textbf{Q2.}
%
\ul{
Tables are hard to grasp at a first glance due to too many abbreviations and
notations.
}

\noindent\textbf{A:} Thanks for the suggestion.
In the next revision, we will (1) extend the captions to make them
self-explanatory; (2) repeat the definitions of symbols and abbreviations in
captions; (3) highlight the columns for important performance metrics
(\emph{i.e.}, R@1 and ERS); (4) colorize the abbreviations for different
defense methods in the same color as their corresponding legends in the
performance curve figures.

\noindent\textbf{Q3.}
%
\ul{
Comparison in memory and time complexity between defense methods is missing. Are they all
equal?
}

\noindent\textbf{A:}
%
They have same complexity polynomials in terms of time and space.
%
We conduct experiments with two ``Nvidia TITAN Xp'' GPUs on the CUB dataset
with $\eta{=}32$, as follows:
%
\noindent%
\resizebox{1.0\columnwidth}{!}{
\begin{tabular}{c|c|c|c|c}
	\toprule
	 & EST[$\mathcal{S}$]
	 & ACT[$\mathcal{S}$]
	 & HM[$\mathcal{S},g_\mathsf{LGA}$]
	 & HM[$\mathcal{S},g_\mathsf{LGA}$]\&ICS \\
	 \midrule
	Time Complexity
	& $\mathcal{O}(\eta D + 1)$
	& $\mathcal{O}(\eta D + 1)$
	& $\mathcal{O}(\eta D + 1)$
	& $\mathcal{O}(\eta D + 1)$\\
	Actual Training Time
	& 8.4 hour 
	& hour
	& 9.1 hour
	& 9.4 hour \\
	\hline
	Space Complexity 
	& $\mathcal{O}(\eta D + 1)$
	& $\mathcal{O}(\eta D + 1)$
	& $\mathcal{O}(\eta D + 1)$
	& $\mathcal{O}(\eta D + 1)$\\
	GPU Memory Usage 
	& 6559 MB
	& 6617 MB
	& 6657 MB
	& 8385 MB\\
	\bottomrule
\end{tabular}
	}
%
The PGD complexities per adversarial
example are identical across different defenses.
%
Triplet sampler is aligned in the table for identical
sampling complexities.
%
Omitting the identical terms, the rest complexity stems from adversarial perturbation objective functions and loss function.
%
The reported values are uneasy to compare for future work as they are sensitive
to hardware, software, and programming tricks.
%
The paragraph will be provided in the next revision.

### 2022-01-30 reb/RebuttalTemplate.tex

\noindent\textbf{Q2.}
%
\ul{
Tables are hard to grasp at a first glance due to too many abbreviations and
notations.
}

\noindent\textbf{A:} Thanks for the suggestion.
In the next revision, we will (1) extend the captions to make them
self-explanatory; (2) repeat the definitions of symbols and abbreviations in
captions; (3) highlight the columns for important performance metrics
(\emph{i.e.}, R@1 and ERS); (4) colorize the abbreviations for different
defense methods in the same color as their corresponding legends in the
performance curve figures.

\noindent\textbf{Q3.}
%
\ul{
Comparison in memory and time complexity between defense methods is missing. Are they all
equal?
}

\noindent\textbf{A:}
%
They have same complexity polynomials in terms of time and space.
%
We conduct experiments with two ``Nvidia TITAN Xp'' GPUs on the CUB dataset
with $\eta{=}32$, as follows:
%
\noindent%
\resizebox{1.0\columnwidth}{!}{
\begin{tabular}{c|c|c|c|c}
	\toprule
	 & EST[$\mathcal{S}$]
	 & ACT[$\mathcal{S}$]
	 & HM[$\mathcal{S},g_\mathsf{LGA}$]
	 & HM[$\mathcal{S},g_\mathsf{LGA}$]\&ICS \\
	 \midrule
	Time Complexity
	& $\mathcal{O}(\eta D + \eta)$
	& $\mathcal{O}(\eta D + \eta)$
	& $\mathcal{O}(\eta D + \eta)$
	& $\mathcal{O}(\eta D + \eta)$\\
	Actual Training Time
	& 8.4 hour 
	& hour
	& 9.1 hour
	& 9.4 hour \\
	\hline
	Space Complexity 
	& $\mathcal{O}(\eta D + 1)$
	& $\mathcal{O}(\eta D + 1)$
	& $\mathcal{O}(\eta D + 1)$
	& $\mathcal{O}(\eta D + 1)$\\
	GPU Memory Usage 
	& 6559 MB
	& 6617 MB
	& 6657 MB
	& 8385 MB\\
	\bottomrule
\end{tabular}
	}
%
The PGD complexities per adversarial
example are identical across different defenses.
%
Triplet sampler is aligned in the table for identical
sampling complexities.
%
Omitting the identical terms, the rest complexity stems from adversarial perturbation objective functions and loss function.
%
The reported values are uneasy to compare for future work as they are sensitive
to hardware, software, and programming tricks.
%
The paragraph will be provided in the next revision.

### 2022-01-30 reb/RebuttalTemplate.tex

\noindent\textbf{Q2.}
%
\ul{
Tables are hard to grasp at a first glance due to too many abbreviations and
notations.
}

\noindent\textbf{A:} Thanks for the suggestion.
In the next revision, we will (1) extend the captions to make them
self-explanatory; (2) repeat the definitions of symbols and abbreviations in
captions; (3) highlight the columns for important performance metrics
(\emph{i.e.}, R@1 and ERS); (4) colorize the abbreviations for different
defense methods in the same color as their corresponding legends in the
performance curve figures.

\noindent\textbf{Q3.}
%
\ul{
Comparison in memory and time complexity between defense methods is missing. Are they all
equal?
}

\noindent\textbf{A:}
%
They have same complexity polynomials in terms of time and space.
%
We conduct experiments with two ``Nvidia TITAN Xp'' GPUs on the CUB dataset
with $\eta{=}32$, as follows:
%
\noindent%
\resizebox{1.0\columnwidth}{!}{
\begin{tabular}{c|c|c|c|c}
	\toprule
	 Defense Method
	 & EST[$\mathcal{S}$]
	 & ACT[$\mathcal{S}$]
	 & HM[$\mathcal{S},g_\mathsf{LGA}$]
	 & HM[$\mathcal{S},g_\mathsf{LGA}$]\&ICS \\
	 \midrule
	Time Complexity
	& $\mathcal{O}(\eta D + \eta + 1)$
	& $\mathcal{O}(\eta D + \eta + 1)$
	& $\mathcal{O}(\eta D + \eta + 1)$
	& $\mathcal{O}(\eta D + \eta + 1)$\\
	Actual Training Time
	& 8.4 hour 
	& 9.3 hour
	& 9.1 hour
	& 9.4 hour \\
	\hline
	Space Complexity 
	& $\mathcal{O}(D + 1)$
	& $\mathcal{O}(D + 1)$
	& $\mathcal{O}(D + 1)$
	& $\mathcal{O}(D + 1)$\\
	GPU Memory Usage 
	& 6559 MB
	& 6617 MB
	& 6657 MB
	& 8385 MB\\
	\bottomrule
\end{tabular}
	}
%
The PGD complexities per adversarial
example are identical across different defenses.
%
Triplet sampler is aligned in the table for identical
sampling complexities.
%
Omitting the identical terms, the rest complexity stems from adversarial perturbation objective functions and loss function.
%
The reported values are uneasy to compare for future work as they are sensitive
to hardware, software, and programming tricks.
%
The paragraph will be provided in the next revision.

### 2022-01-31 reb/RebuttalTemplate.tex

\noindent\textbf{Q1.}
%
\ul{
The DML models are not special in terms of robustness against
adversarial attacks compared to other deep models.
}

\noindent\textbf{A:} 
%
We agree with the reviewer. Robustness at the visual representation level
remains an open problem. Since DML can be interpreted as ``representation
learning in metric space'' and inspire visual representation learning, we
believe the defense for DML is one step closer to the representation-level
robustness disentangled from specific tasks.

\noindent\textbf{Q2.}
%
\ul{
The relationship between the proposed method and a series of
adversarial training algorithms}~\cite{smoothat,currat,optcontrolaml}.

\noindent\textbf{A:}
%
CAT~\cite{currat} uses adversarial examples with gradually increasing strength
(\emph{i.e.}, PGD step), while our LGA gradually increases destination hardness
$H_\mathsf{D}$ (with a fixed PGD step).
%
SAT~\cite{smoothat} gradually increases the difficulty of adversarial examples
in order to achieve smoothness of loss landscape, while our HM is similar to
``early termination of PGD''~\cite{smoothat} with a dynamic ``termination''
threshold determined by LGA.
%
Zhu~\emph{et al.}~\cite{optcontrolaml} presents an optimal control view of
adversarial machine learning, where our method can also be interpreted as
``adversarial training against test-time attack''.
%
Although they do not mention DML, the similarities will be included in
introduction and related work sections in our revised version.

@@

%\subsubsection*{To Reviewer \#2}
\vspace{0.3em}
\noindent\textbf{To Reviewer \#2}\vspace{0.3em}

\noindent\textbf{Q1.}
%
\ul{
Sentences tend to be too long and complex; Method abbreviations are confusing
and hard to remember.
}

\noindent\textbf{A:} Thanks for the suggestion. We will polish the sentences to make
them shorter and simpler, as well as use better abbreviations in the 
revised version.

@@

\noindent\textbf{Q2.}
%
\ul{
Tables are hard to grasp at a first glance due to too many abbreviations and
notations.
}

\noindent\textbf{A:} Thanks for the suggestion.
In the next revision, we will (1) extend the captions to make them
self-explanatory; (2) repeat the definitions of symbols and abbreviations in
captions; (3) highlight the columns for important performance metrics
(\emph{i.e.}, R@1 and ERS); (4) colorize the abbreviations for different
defense methods in the same color as their corresponding legends in the
performance curve figures.

\noindent\textbf{Q3.}
%
\ul{
Comparison in memory and time complexity between defense methods is missing. Are they all
equal?
}

\noindent\textbf{A:}
%
They have the same complexity polynomials in terms of time and space.
%
We conduct experiments with two ``Nvidia TITAN Xp'' GPUs on the CUB dataset
with $\eta{=}32$, as follows:
%
\noindent%
\resizebox{1.0\columnwidth}{!}{
\begin{tabular}{c|c|c|c|c}
	\toprule
	 Defense Method
	 & EST[$\mathcal{S}$]
	 & ACT[$\mathcal{S}$]
	 & HM[$\mathcal{S},g_\mathsf{LGA}$]
	 & HM[$\mathcal{S},g_\mathsf{LGA}$]\&ICS \\
	 \midrule
	Time Complexity
	& $\mathcal{O}(\eta D + \eta + 1)$
	& $\mathcal{O}(\eta D + \eta + 1)$
	& $\mathcal{O}(\eta D + \eta + 1)$
	& $\mathcal{O}(\eta D + \eta + 1)$\\
	Actual Training Time
	& 8.4 hour 
	& 9.3 hour
	& 9.1 hour
	& 9.4 hour \\
	\hline
	Space Complexity 
	& $\mathcal{O}(D + 1)$
	& $\mathcal{O}(D + 1)$
	& $\mathcal{O}(D + 1)$
	& $\mathcal{O}(D + 1)$\\
	GPU Memory Usage 
	& 6559 MB
	& 6617 MB
	& 6657 MB
	& 8385 MB\\
	\bottomrule
\end{tabular}
	}
%
The PGD complexities per adversarial
example are identical across different defenses.
%
Triplet sampler is aligned in the table for identical
sampling complexities.
%
Omitting the identical terms, the remaining complexity stems from adversarial perturbation objective functions and loss function.
%
The reported values are difficult to compare for future work as they are sensitive
to hardware, software, and programming tricks.
%
The paragraph will be provided in the revised version.

@@

\noindent\textbf{Q2.}
%
\ul{Tables (e.g., Tab.~3) are hard to read.}

\noindent\textbf{A:} Thanks for the suggestion. We will improve the tables as described in the answer to Q2 of Reviewer \#2.

\noindent\textbf{Q3.}
%
\ul{The performance on benign examples seems to drop a lot. Does it mean the
HM is just another trade-off way?}

\noindent\textbf{A:}
%
Performance drop on benign example is inevitable for adversarial training
\cite{madry,trades,awp,advrank,robrank}, and the trade-off exists
between benign example performance and robustness via hyper-parameters
(\emph{e.g.}, $\varepsilon$).
%
Our method is not a trade-off way of dealing with this problem, because a trade-off method cannot
simultaneously achieve higher robustness, training efficiency, and benign
example performance than previous state-of-the-arts~\cite{advrank,robrank}.
